Preferential Accretion in the SMBH of Milky Way Size Galaxies Due to Direct Feeding by Satellites

### 2017-01-24 ms.tex
Final edits for resubmission

\shorttitle{Gas Accretion in MW-like Galaxies}
\shortauthors{N. N. Sanchez, J. M. Bellovary, \& K. Holley-Bockelmann}

@@

\title{Cosmological Hydrodynamic Simulations of Preferential Accretion in the SMBH of Milky Way Size Galaxies}
%\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}

@@

Using a new, high-resolution cosmological hydrodynamic simulation of a Milky Way-type (MW-type) galaxy, we explore how a merger-rich assembly history affects the mass budget of the central supermassive black hole (SMBH). We examine a MW-mass halo at the present epoch whose evolution is characterized by several major mergers to isolate the importance of merger history on black hole accretion. This study is an extension of Bellovary et. al. 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole reflects what is accreted by the host galaxy halo. In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas. Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy through the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH. Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH. In addition, the presence of mergers, particularly major mergers, also helps funnel low angular momentum gas more readily to the center of the galaxy. Our results imply that galaxy mergers play an important role in feeding the SMBH in MW-type galaxies with merger-rich histories.

@@

\section{Introduction}\label{sec-intro}

Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}. In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Begelman1980,Alexander2005,Papovich2006,Volonteri2012}. The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together \citep{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Micic2011,Mullaney2012}.

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects \citep{Ferrarese2000,Gebhardt2000}. A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep[e.g.][]{Merritt2001,Tremaine2002,Graham2011,Mcconnell2013}. Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011,Emsellem2011,Dubois2015}. However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}. One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep[e.g.][]{DiMatteo2005,Shen2008}. Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy \citep{Schawinski2010}.

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides \citep[e.g.][]{Richards2006,Reddy2008,Hopkins2010}. Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred \citep{Treister2012}. Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.

@@

Our simulation introduces a uniform UV background at z$\sim$9 to simulate the cosmic reionization energy energy using the formula of \cite{Haardt2012}. To model star formation, we stochastically turn gas particles into stars with a efficiency of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K). These star particles represent a Kroupa initial mass function \citep{Kroupa1993}. Molecular hydrogen and metal-line cooling are not included, though we implement a low-temperature extension to the cooling curve to trace metals \citep{Bromm2001} and the metal diffusion prescription of \cite{Shen2010}.

Supernova feedback releases $10^{51}$ ergs of thermal energy within a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation. SN Ia and II rates from \cite{Thielemann1986} and \cite{Woosley1995}, respectively, are implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities. Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}.

Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007,Christensen2015}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}. The parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}. Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.

@@

Black hole mergers occur when they are separated by less than twice the softening length and satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$ (which is an approximation of being gravitationally bound),  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via mergers, black holes accrete through the Bondi-Hoyle mechanism:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{\rm BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}
where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, and $v$ is the black hole's relative velocity to the gas. Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively. This energy is distributed as thermal energy to the 32 nearest particles via a kernel probability function. Though other groups use a higher value for feedback, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces massive black holes (MBHs) in better agreement with MBH-host galaxy scaling relations. However, as our main concern is in the relative proportion of gas  from various origins (See \ref{results}), our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$. This same model was additionally used by \cite{Bellovary2013} at a lower resolution and without the addition of the dynamical friction prescription.

@@

We first identify halos using the Amiga Halo Finder which uses an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004} to set the virial radius in the primary halo. We select the primary halo to be the most massive at z=0 in the high resolution region. The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$.

@@

However, as we discussed in Section 1, if the galaxy halo is $\gtrsim$ 10$^{11}$ M$_{\odot} $, the gas is known to shock-heat to the virial temperature of the halo. We identify shocked particles through an increase in entropy and temperature using the following criteria:
\begin{equation}
T_{\rm shock} \geq 3/8 T_{\rm vir},
\end{equation}
where T$_{\rm vir}$ is the virial temperature of the halo, T$_{\rm shock}$ is the temperature of the gas particle, and 
\begin{equation}
\Delta S \geq S_{\rm shock} - S_0,
\end{equation}
where S$_0$ is the initial entropy of the gas particle, and 
\begin{equation}
S_{\rm shock} = log_{10}[3/8 T_{\rm vir}^{1.5}/4 \rho_0],
\end{equation}
where $\rho_0$ is the gas density prior to the shock. Since our halo is $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo at later times.

@@

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime.pdf}}}
\caption[]{The central BH's cumulative mass as a function of time and redshift. The black dashed line indicates the total cumulative BH mass. The black solid line indicates the total accreted gas mass. The blue dot-dashed line indicates smoothly accreted gas mass that remains unshocked after entering the virial radius of the main halo. The green solid line indicates the gas mass accreted through mergers. The red dashed line indicates accreted gas mass that was shocked upon entry into the halo.}
\label{hrh258allmassgas} 
\end{figure}

@@

The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 (mass ratio, q $\sim$ 0.8) and the second at z $\sim$ 1.2 (q $\sim$ 1). Despite its merger-rich history, gas accretion smoothly increases the cumulative black hole mass in h258 throughout its evolution as can be seen in Figure \ref{hrh258allmassgas}. The black dashed line in \ref{hrh258allmassgas} indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass. The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively. It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed. This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}. Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1. It is clear that unshocked gas makes up the majority entering the galaxy at early times. However, the transition between when smooth, unshocked accretion and mergers dominate are clearly distinguished. While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.

This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}). Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy and the SMBH at z=0, again differentiated by gas origin. The gas accreted by the galaxy is half (56 $\%$) comprised of merger gas, with 36 $\%$ of the gas entering through unshocked, smooth accretion. The smallest fraction of the total gas is comprised of shocked gas (8 $\%$ ). Unlike the galaxy, nearly three quarters (74 $\%$) of the gas accreted by the central SMBH was accreted via mergers, while only a quarter (24 $\%$ ) is comprised of unshocked, smoothly accreted gas. Shocked gas makes up the last 2$\%$ of total gas entering the SMBH. \textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same. Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.

@@

A previous study by \cite{Fu2007} supplies direct observational evidence that gas from a merger can be funneled directly into the vicinity of the SMBH (\textless 1 pc). Their study examined a collection of twelve low-redshift quasars, half of which are characterized by luminous extended emission-line regions (EELRs). These EELRs were found to have metallicities below the mass-metallicity correlation of normal galaxies and are thought to have resulted from massive, galactic superwinds accompanying the creation of the powerful radio jets associated with the quasars. The quasars hosting EELRs were also found to have low-metallicity broad-line regions (BLRs) at their centers, while the quasars without EELRs hosted BLRs with metallicities above Z$_{\odot}$. \cite{Fu2007} determined that the presence of these low-metallicity EELRs as well as the similar, low-metallicity BLRs are evidence of a merger with a gas-rich galaxy. Such an interaction may explain both the infusion of low-metallicity gas into the BLRs and the subsequent ejection of that gas by the radio jets, forming the EELRs.  While our study did not measure metallicity or include radio jets, our overall results support the conclusion of a major merger funneling gas into the center of a galaxy.

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096.pdf}}}
\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto h258.  Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines). The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
\label{hrh258angmom} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584.pdf}}}
\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2). The major merger is occurring at this time and about 450,000 gas particles accreted onto the halo at this timestep. Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively. The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
\label{hrh258angmom_merger2} 
\end{figure}

To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of the gas at the moment it enters the halo. Figure \ref{hrh258angmom} shows a cumulative distribution of the angular momentum of the gas as it enters the halo (solid lines). We further distinguish the gas that enters the SMBH (dashed lines), still considering its angular at the moment of halo entry. The gas is again distinguished by origin (clumpy, unshocked, shocked being green, blue, and red, respectively). We find that the angular momentum of gas entering which eventually reaches the SMBH is lower overall, and that the lowest angular momentum gas is comprised of both clumpy and unshocked gas. This result can be seen in Figure \ref{hrh258angmom_merger2}, which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the most massive merger at z $\sim$ 1.2. (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum. This influx of clumpy gas primarily had its origins in the secondary halo. Examining the angular momentum of all the gas entering from the secondary halo, we found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.  Thus it appears that gas from the secondary galaxy may be directly channeled into the SMBH of the primary, in addition to the standard picture of gas in the host galaxy which loses angular momentum due to torques from the merger dynamics \citep{Capelo2015},

@@

\section{Conclusion}
%\textcolor{violet}{
This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past. We trace the gas into the SMBH at its center and differentiate the gas accreted onto the galaxy and SMBH by origin. Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is separated into ``shocked'' and ``unshocked'' categories. Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
%}

>>>>

\shorttitle{Gas Accretion in MW-like Galaxies}
\shortauthors{Sanchez et. al.}

@@

\title{Preferential Accretion in the SMBH of Milky Way Size Galaxies Due to Direct Feeding by Satellites}
%\title{A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies}

@@

Using a new, high-resolution cosmological hydrodynamic simulation of a Milky Way-type (MW-type) galaxy, we explore how a merger-rich assembly history affects the mass budget of the central supermassive black hole (SMBH). We examine a MW-mass halo at the present epoch whose evolution is characterized by several major mergers to isolate the importance of merger history on black hole accretion. This study is an extension of Bellovary et. al. 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole reflects what is accreted by the host galaxy halo. In this study, we find that a merger-rich galaxy will have a central SMBH preferentially fed by merger gas. Moreover, we find that nearly 30$\%$ of the accreted mass budget of the SMBH enters the galaxy directly from satellites during the two major mergers in its history, which may account for the increase of merger-gas fueling the SMBH. Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH. In addition, the presence of mergers, particularly major mergers, also helps funnel low angular momentum gas more readily to the center of the galaxy. Our results imply that galaxy mergers play an important role in feeding the SMBH in MW-type galaxies with merger-rich histories.

@@

\section{Introduction}\label{sec-intro}
Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies \citep[see][for a review]{Kormendy2013}. In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence \citep{Begelman1980,Alexander2005,Papovich2006,Volonteri2012}. The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together \citep{Haehnelt2000,DiMatteo2005,Hopkins2006,Fu2008,Sijacki2009,Silverman2009,Micic2011,Mullaney2012}.

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects \citep{Ferrarese2000,Gebhardt2000}. A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass \citep[e.g.][]{Merritt2001,Tremaine2002,Graham2011,Mcconnell2013}. Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside \citep{VanDenBosch2007,Moster2010,Natarajan2011,Emsellem2011,Volonteri2016}. However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation \citep{Micic2007,Volonteri2009,Reines2013,Graham2014}. One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges \citep[e.g.][]{DiMatteo2005,Shen2008}. Major mergers are thought to supply gas to the central SMBH resulting in feedback which quenches star formation and affects the structure of the galaxy \citep{Schawinski2010}.

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred \citep{Treister2012}. Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes \citep{Ellison2010}.

These major mergers can also strongly disturb gas-rich galaxies producing resonant tidal torques that allow large influxes of material to funnel directly into the center, fueling bursts of star formation and SMBH accretion \citep[e.g.][]{Sanders1988,Sanders1996,Barnes1991,Mihos1996,Hopkins2006,Richards2006,Reddy2008,Hopkins2010}. At small scales closer to the SMBH, the larger tidal torques from a major merger less effectively drive gas into the inner most region of the galaxy; however, perturbations at all scales from the merger could still drive accretion into the smaller inner region of galaxy, though the rapid decay of these perturbations may not encourage gas flow. Other large scale instabilities such as bars and spiral waves are also proficient fueling mechanisms for funneling gas into the galaxy; however, these cases can inhibit small scale gas accretion through other complications. While there is still some uncertainty regarding the processes that transport gas through last $\sim$ 1 kpc to the SMBH, \cite{Hopkins2010} has shown that major mergers between gas-rich galaxies can result in non-axisymmetric gravitational instabilities which can drive BH accretion within the inner most $\sim$ 0.1 pc.

@@

Our simulation introduces a uniform UV background at z$\sim$9 to simulate the cosmic reionization energy energy using the formula of \cite{Haardt2012}. To model star formation, we stochastically turn gas particles into stars with a star formation efficiency parameter of c$^*$ = 0.1 once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K). As shown in \citet{Governato2009a}, this high density threshold is necessary to produce bursty star formation events in the high-density peaks of the ISM.  Realistic star formation histories result in galaxies which have realistic density profiles and lie on the observed scaling relations (mentioned in detail below).  The lower-resolution simulations mentioned in this paper have a lower threshold, since the high density peaks are not resolved.
These star particles represent a Kroupa initial mass function \citep{Kroupa1993}.  Molecular hydrogen and metal-line cooling are not included, though we implement a low-temperature extension to the cooling curve to trace metals \citep{Bromm2001} and the metal diffusion prescription of \cite{Shen2010}.

Supernova (SN) feedback releases $10^{51}$ ergs of thermal energy within a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation. SN Ia and II rates from \cite{Thielemann1986} and \cite{Woosley1995}, respectively, are implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities. Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}. While it is true that a different treatment of the ISM and SNe feedback might alter the structure of the ISM, \cite{Christensen2014} examined simulated spiral and dwarf galaxies utilizing similar SNe prescriptions and three different ISM models, and determined that the resulting ISM remained consistent with each other. Additionally, our galaxy is in good agreement with galaxies affected by superbubble SN feedback \citep{Keller2014}.

Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007,Christensen2015}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}. The parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}. Given that the simulations are in accordance with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH.

@@

Black hole mergers occur when they are separated by less than twice the softening length and satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$ (which is an approximation of being gravitationally bound),  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via mergers, black holes accrete through the Bondi-Hoyle mechanism:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{\rm BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}
where $\alpha$ is a constant of order 1, $\rho$ is the density of the surrounding gas, $c_s$ is the sound speed, $v$ is the black hole's relative velocity to the gas, and the accretion rate is Eddington-limited. Feedback is applied to surrounding gas with an energy boost determined by the accreted mass as follows: $\dot{E}$ = $\epsilon _{r}$$\epsilon_{f}$$\dot{M}$$c^2$ where $\dot{M}$ is the accreted mass, and $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ are assumed for the radiative efficiency and feedback efficiency, respectively. This energy is distributed as thermal energy to the 32 nearest particles via a kernel probability function. Though other groups use a higher value for feedback, $\epsilon _f = 0.05$ \citep{Sijacki2007,DiMatteo2008}, we find that $\epsilon_f = 0.03$ in our code produces massive black holes (MBHs) in better agreement with MBH-host galaxy scaling relations. However, as our main concern is in the relative proportion of gas from various origins (See \ref{results}) and we restrict our analysis of the angular momentum of gas to only the timestep of entry into the main halo, our results are not sensitive to our choices of $\epsilon _{r}$ or $\epsilon_{f}$. This same model was additionally used by \cite{Bellovary2013} at a lower resolution and without the addition of the dynamical friction prescription.

@@

We first identify halos using the Amiga Halo Finder which uses an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004} to set the virial radius in the primary halo. We select the primary halo to be the most massive at z=0 in the high resolution region. The central SMBH in the primary halo has a mass of $1.3 \times 10^{7} M_{\odot}$ and a velocity dispersion in the bulge of $\sigma$ $\sim$ 152 km s$^{-1}$, indicating that h258 lies on the M-$\sigma$ relation.

@@

However, as we discussed in Section 1, if the galaxy halo is $\gtrsim$ 10$^{11}$ M$_{\odot} $, the gas is known to shock-heat to the virial temperature of the halo. We identify shocked particles through an increase in entropy and temperature using the following criteria:
\begin{equation}
T_{\rm shock} \geq 3/8 T_{\rm vir},
\end{equation}
where T$_{\rm vir}$ is the virial temperature of the halo, T$_{\rm shock}$ is the temperature of the gas particle, and 
\begin{equation}
\Delta S \geq S_{\rm shock} - S_0,
\end{equation}
where S$_0$ is the initial entropy of the gas particle, and 
\begin{equation}
S_{\rm shock} = log_{10}[3/8 T_{\rm vir}^{1.5}/4 \rho_0],
\end{equation}
where $\rho_0$ is the gas density prior to the shock. Since our halo is $\sim$ 10$^{12}$ M$_{\odot} $ by z = 0, we should expect to find more shocked gas entering the halo at later times. Both types of smoothly accreted gas are tracked until they reach a cutoff radius at 10$\%$ of the virial radius (0.1 R$_{vir}$) at which point supernova feedback may appear as virial shocking and cause contamination in our estimates of shocked accretion. This cutoff also accounts for any AGN feedback we might encounter.

@@

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_massgastime_hashed.pdf}}}
\caption[]{The central BH's cumulative mass as a function of time and redshift. The black dashed line indicates the total cumulative BH mass. The black solid line indicates the total accreted gas mass. The blue dot-dashed line indicates smoothly accreted gas mass that remains unshocked after entering the virial radius of the main halo. The green solid line indicates the gas mass accreted through mergers. The red dashed line indicates accreted gas mass that was shocked upon entry into the halo. Major mergers are marked with grey hatched regions.}
\label{hrh258allmassgas} 
\end{figure}

@@

The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 (mass ratio, q $\sim$ 0.8) and the second at z $\sim$ 1.2 (q $\sim$ 1). Despite its merger-rich history, gas accretion smoothly increases the cumulative black hole mass in h258 throughout its evolution as can be seen in Figure \ref{hrh258allmassgas}. The black dashed line in \ref{hrh258allmassgas} indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass. The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively. Major mergers are indicated by grey hatched regions. It is worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed. This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}. Aside from this early BH assembly, the largest gain in accreted SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1. We know unshocked gas makes up the majority of accreted mass entering the galaxy at early times; however, the transition between when smooth, unshocked accretion and merger gas dominates are clearly distinguished. While clumpy gas (green) dominates gas mass accretion in the SMBH at the earliest time, unshocked gas (blue) overtakes it for a short time before clumpy gas once again dominates by z $\sim$ 1.5.

This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the accreted mass fractions in the SMBH (Figure \ref{hrh258stackfrac}). Figure \ref{hrh258stackfrac} depicts the fractions of total gas accretion in the galaxy and the SMBH at z=0, again differentiated by gas origin. The gas accreted by the galaxy is half (56 $\%$) comprised of merger gas, with 36 $\%$ of the gas entering through unshocked, smooth accretion. The smallest fraction of the total gas is comprised of shocked gas (8 $\%$ ). Unlike the galaxy, nearly three quarters (74 $\%$) of the gas accreted by the central SMBH was accreted via mergers, while only a quarter (24 $\%$ ) is comprised of unshocked, smoothly accreted gas. Shocked gas makes up the last 2$\%$ of total gas entering the SMBH. \textit{It is evident then that the SMBH more readily accretes gas gained through mergers.} While this result is consistent with the work of \cite{Dubois2015} which explores how galaxy mergers may be necessary for triggering black hole growth in low mass galaxies, it is contrary to \cite{Bellovary2013} which found that in high redshift, high mass galaxies, the fractions of gas comprising the SMBH and its host were nearly the same. Through our results, it appears that when major mergers are a key part of the galaxy assembly history, these mergers may also drive SMBH growth.

@@

A previous study by \cite{Fu2007} supplies direct observational evidence that gas from a merger can be funneled directly into the vicinity of the SMBH (\textless 1 pc). Their study examined a collection of twelve low-redshift quasars, half of which are characterized by luminous extended emission-line regions (EELRs). These EELRs were found to have metallicities below the mass-metallicity correlation of normal galaxies and are thought to have resulted from massive, galactic superwinds accompanying the creation of the powerful radio jets associated with the quasars. The quasars hosting EELRs were also found to have low-metallicity broad-line regions (BLRs) at their centers, while the quasars without EELRs hosted BLRs with metallicities above Z$_{\odot}$. \cite{Fu2007} determined that the presence of these low-metallicity EELRs as well as the similar, low-metallicity BLRs are evidence of a merger with a gas-rich galaxy. Such an interaction may explain both the infusion of low-metallicity gas into the BLRs and the subsequent ejection of that gas by the radio jets, forming the EELRs.  While our study did not measure metallicity or include radio jets, our overall results support the conclusion that a majority of the gas from the secondary and tertiary galaxy mergers directly fuel the SMBH at the center of the primary galaxy.

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_cumu_4096_legend.pdf}}}
\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto h258 by z = 0.  Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines). The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
\label{hrh258angmom} 
\end{figure}

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_am_tsnew_1584_legend.pdf}}}
\caption[]{ Normalized cumulative distribution of angular momentum (kpc km s${{-1}}$) of the gas particles accreted onto the h258 galaxy at a single timestep (z $\sim$ 1.2) during the major merger's greatest influx of accreted gas. About 450,000 gas particles accreted onto the halo at this timestep. Angular momentum of gas particles accreted onto the main halo and central black hole are distinguished by solid and dashed lines, respectively. The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
\label{hrh258angmom_merger2} 
\end{figure}

To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of the gas at the moment it enters the halo. Figure \ref{hrh258angmom} shows a cumulative distribution of the angular momentum of the gas as it enters the halo (solid lines). We further distinguish the gas that enters the SMBH (dashed lines), still considering its angular momentum at the moment of halo entry. The gas is again distinguished by origin (clumpy, unshocked, shocked being green, blue, and red, respectively). We find that the angular momentum of gas entering which eventually reaches the SMBH is lower overall, and that the lowest angular momentum gas is comprised of both clumpy and unshocked gas. This result can be seen in Figure \ref{hrh258angmom_merger2}, which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the greatest influx of accreted gas during the merger at z $\sim$ 1.2. (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum. This influx of clumpy gas primarily had its origins in the secondary halo. Examining the angular momentum of all the gas entering from the secondary halo, we found that it was consistent with the angular momentum of the total clumpy gas entering the main halo.  Thus it appears that gas from the secondary galaxy may be directly channeled into the SMBH of the primary, in addition to the standard picture of gas in the host galaxy which loses angular momentum due to torques from the merger dynamics \citep{Capelo2015},

@@

\section{Conclusion}
This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past. We trace the gas into the SMBH at its center and differentiate the gas accreted onto the galaxy and SMBH by origin. Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is separated into ``shocked'' and ``unshocked'' categories. Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.

A previous study by \cite{Bellovary2013} analyzed high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host. Contrary to these previous results, when we examined a galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers. This remained true both in an older low resolution simulation of the same galaxy as well as this current iteration. \textit{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.} We also note that in the high resolution case, we can attribute the increase of clumpy gas to the major mergers that characterize h258.
